\documentclass[12pt]{article}
\usepackage{graphicx}    % needed for including graphics e.g. EPS, PS
 \topmargin -1.5cm        % read Lamport p.163
 \oddsidemargin -0.04cm   % read Lamport p.163
 \evensidemargin -0.04cm  % same as oddsidemargin but for left-hand pages
 \textwidth 16.59cm
 \textheight 21.94cm 
 \pagestyle{empty}       % Uncomment if don't want page numbers
 \parskip 7.2pt           % sets spacing between paragraphs
 %\renewcommand{\baselinestretch}{1.5} % Uncomment for 1.5 spacing between lines
 \parindent 0pt  % sets leading space for paragraphs




\begin{document}
\section{Assignment 3}


1.  This program consists of an appender, extracter, tables, write header, and \
initate header functions.  Append makes use of stat and file pointers.  Extract\
 also makes use of file pointers.  Tables makes use of the ctime.  Remove and append all were not implemented.

2.  The first functionality of my project to be finished was append, then came extract, and then tables.   

3.  Learning how to use Latex for one. I've learned to make better use of my time, and start this assignments much earlier. This was the most ambitious project I've worked on so far.  Particularly interesting because it is a simple project.

4.  
\begin{itemize}
\item a. to learn about system calls and i/o.
\item b. For append, I would check if it were compatible with ar.  For extract, I would check the actual contents of the extracted file.  For the tables, I would check the output against the actual output of the t and tv modes of ar.
\item c. To start the assignments earlier.  Design my project with greater detail before coding.  Ask for help sooner. 
\end{itemize}
\end{document}
